Collaborative Multi-output Gaussian Processes

### 2014-06-11 paper/intro.tex
related work

% Some citations that can be brought back somewhere
%The traditional approach in multiple GP regression has been to mix independent latent processes to generate correlated functions.
%The mixing can be a weighted linear combinations with fixed \citep{teh-et-al-aistats-05,bonilla-et-al-nips-08} or input-dependent \citep{wilson-et-al-icml-12,nguyen2013efficient} coefficients or convolution of processes \citep{boyle-frean-nips-05,alvarez-lawrence-nips-08}.
%The correlations of the outputs are induced through sharing of these base processes.

>>>>

% Some citations that can be brought back somewhere
\paragraph{Related work}
Most GP-based multi-output models create correlated outputs by mixing a set of one or more independent latent processes.
The mixing can be a linear combinations with fixed coefficients \citep[see e.g.][]{teh-et-al-aistats-05,bonilla-et-al-nips-08}; this is known in the geostatistics community as ''linear model of coregionalization'' \citep{goovaerts1997geostatistics}.
Such models may also be reformulated in a common Bayesian framework, for example by placing a spike and slab prior over the coefficients \citep{titsias2011spike}.
More complex dependencies can be induced by using 
 input-dependent coefficients \citep{wilson-et-al-icml-12,nguyen2013efficient}  or convolving processes \citep{boyle-frean-nips-05,alvarez-lawrence-nips-08,alvarez2010efficient}.

While we also use the mixing construction, the key difference in our model is the role of inducing variables.
In particular, when used in previous models to reduce the computational costs \citep[see e.g.][]{alvarez-lawrence-nips-08,alvarez2010efficient}, the inducing points are integrated out or collapsed. 
In contrast, our model maintains an explicit representation of the posterior over the inducing variables that is learned using data from all outputs.
The explicit representation furthermore facilitates scalable learning in a similar fashion to \citep{hensmangaussian}, making it applicable to much larger datasets.
